Make any stupid plot you want

### 2020-12-16 draft/sections/math.tex
word soup about nus

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset K$ around every $k$. The inclusion map $\iota: U \rightarrow K$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}

\end{equation}

The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

%not sure what's supposed to happen w/ sheafs here
% add U ^ V + intersection to get section on union which is condition of sheafs. 
\subsection{Prerender Space}
\label{sec:display}

@@

\begin{equation}
     \rho(u, v) = Q(\nu_(\tau_{c_0}), \ldots \nu_param_{n}(\tau_{c_n}))(u,v)
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the y position of a line drawn on screen such that $Q: \nu_{ypos}, \nu_{linewidth} \rightarrow \rho_{Y}$.

@@

\subsubsection{Channels}
Visual channels are mappings from data into visual space, for example distinguishing categories by coloring them differently  \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}. Channels are an example of $\nu: c \mapsto d \in D$, which are the mappings from data $r \in \Gamma(\tau)$ to some part of the prerender fiber $D$. the $\nu$ functions can target only one field in $D$, such as $X$, or multiple such as $R,G,B$.

>>>>

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset K$ around every $k$. The inclusion map $\iota: U \rightarrow K$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

@@

\subsection{Prerender Space}
\label{sec:display}

@@

\begin{equation}
     \rho(u, v) = Q(\nu_{param_{n}}(\tau_{c_0}), \ldots \nu_{param_{n}}(\tau_{c_n}))(u,v)
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the output of the $\rho_y$ y position of a line on screen.

@@

\subsubsection{Channels}
For the aesthetic mapping function $\nu$ to faithfully transform the data in $\xi^*\tau$, the $\nu$ and $\tau$ must be symmetrical under all transformations such that
\begin{equation}
    \nu_{param}(\tau_{})
\end{equation}
